Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-07 paper.qmd
Initial writeup
Added chunck to set up script

@@

```{r}
source("scripts/one_c_shaped_dens_structure/04_gen_error_plots.R")
```

>>>>

```{r}
#| label: import-scripts
source("scripts/one_c_shaped_dens_structure/04_gen_error_plots.R")
```

@@

To illustrate how the methods organise difference number of points within the structure in the NLDR layout, simulated $7\text{-}D$ data having C-shaped structure is used.
